### 2018-10-21 Chapters/Chapter3.tex
graphene

\begin{align*}
\hat{T}_{1n} \hat{T}_{-1(m-n)} &= 0 \\
\hat{T}_{-1(m-n)} \hat{T}_{1n} &= \sum_{\langle i,j \rangle, \sigma_1, \sigma_2} t_{ji,(m-n)} t_{ij,n} \hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1}
\end{align*}

So that,

\begin{equation}
\hat{H}_{eff}(t) = \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = - \frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2}\hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t}
\end{equation}

@@

\begin{align}
J_{ij}(t) &= \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t} \nonumber \\
&= \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n} + t_{ji,-n} t_{ij,(m+n)}}{U+n\omega} \right) e^{im\omega t} \label{Jij1}
\end{align}

@@

\begin{align}
J_{ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{D}_{ij}(t) &= 2it_0\bs{\Delta}_{ij} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
\end{align}

@@

>>>>

\begin{align}
\hat{H}_{\text{eff}}(t) &= \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = -\frac{1}{2}\sum_{mn} \left( \frac{\hat{P}_0  \hat{T}_{-1(m-n)}\hat{T}_{1n}\hat{P}_0}{U+n\omega} + \frac{\hat{P}_0 \hat{T}_{-1n} \hat{T}_{1(m-n)} \hat{P}_0}{U-n\omega} \right) e^{im\omega t} \nonumber \\
&= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}\hat{T}_{1n} + \hat{T}_{-1-n}\hat{T}_{1(m+n)})\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \label{HeffSimplified}
\end{align}

Now, since the hopping operators act on the subspace $d=0$ and must remain within that subspace, thus we can write:

\begin{align*}
\hat{P}_0 \hat{T}_{-1a} \hat{T}_{1b} \hat{P}_0 = \sum_{\langle i,j \rangle, \sigma_1, \sigma_2} t_{ji,a} t_{ij,b} \hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1}
\end{align*}

Where $a$ and $b$ are any two Fourier modes. Inserting this into \ref{HeffSimplified}:

\begin{equation}
\hat{H}_{eff}(t) = \hat{P}_0\hat{H}'^{(2)}(t)\hat{P}_0 = - \frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle, \sigma_1, \sigma_2}\hat{c}_{j \sigma_2}^\dagger \hat{c}_{i \sigma_2} \hat{c}_{i \sigma_1}^\dagger \hat{c}_{j \sigma_1} \frac{t_{ji,(m-n)} t_{ij,n} + t_{ji,(-n)} t_{ij,(m+n)}}{U+n\omega} e^{im\omega t}
\end{equation}

@@

\begin{equation}
J_{ij}(t) = \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n} + t_{ji,-n} t_{ij,(m+n)}}{U+n\omega} \right) e^{im\omega t} \label{Jij1}
\end{equation}

@@

\begin{align}
J_{ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{JijHSOI} \\
\bs{D}_{ij}(t) &= 2it_0\bs{\Delta}_{ij} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \label{DijHSOI}
\end{align}

@@

\input{Chapters/SGraphene}
